Turkey Hemorrhagic Enteritis Virus transcriptome profiling

### 2023-06-19 manuscript_thev_transcriptome.Rmd
Update transcript filter script and manuscript

cov_4hr <- cov_all %>% filter(timepoint == "4hpi") %>%
              select(numreads) %>% pull()
cov_72hr <- cov_all %>% filter(timepoint == "72hpi") %>%
              select(numreads) %>% pull()
cov_72hr <- round(cov_72hr / 1e6, 1)
total_mapped <- round(sum(cov_all$numreads) / 1e6, 1)

>>>>

cov_4hr <- cov_all %>% filter(timepoint == "4hpi") %>%
              select(numreads) %>% pull()
cov_72hr <- cov_all %>% filter(timepoint == "72hpi") %>%
              select(numreads) %>% pull()
cov_72hr <- round(cov_72hr / 1e6, 1)

total_mapped <- round(sum(cov_all$numreads) / 1e6, 1)
